Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-08 paper/main.tex
Usage metrics: kaggle

\paragraph{Kaggle}

@@

@@

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me.
\item I am having second thoughts about keeping the \c{ggplot2} data
  -- it is a big outlier that skews all the graphs...
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\item Add paragraphs for Kaggle and CORE -- only discuss the
  differences from CRAN
\end{itemize}

>>>>

@@

\paragraph{Kaggle} In the Kaggle dataset, \kaggleNbruns packages trigger at least one \eval. In total, \kaggleAllcalls \eval were recorded. Most of them are call to the normal \eval, whereas a few, \kaggleLocals, are calls to \c{local}. They are due to the code loading libraries.
Out of \kaggleStaticeval static \eval sites, we exercise \kaggleTriggeredeval of them. Mot \eval are invoked only once. Only one \eval amounts for several thousand, \kaggleMaxcalls,  invocations. Code amounts for \kaggleCodepercent of arguments in the kaggle corpus. However, contrary to the CRAN corpus, they are all expressions, and there are very few symbols (\kaggleSymbolpercent) and no language objects. Most expression objects result from a call to the \c{parse} function, suggesting that most \eval in Kaggle parse and evaluate strings. The median argument size is \kaggleMedianszeval, which makes sense, as there are very few arguments that are only symbols. The largest argument size is \kaggleMaxszeval. The distribution of events is similar to the one for CRAN: \kaggleSmalleventspct of \eval calls amount for less than 50 events.

\paragraph{Discussion}

@@

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me.
\item I am having second thoughts about keeping the \c{ggplot2} data
  -- it is a big outlier that skews all the graphs...
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\end{itemize}
